% !TEX root = ../SU2-Scitech15.tex

\section{Physical Problem and Numerical Tools}

In this section, the main numerical algorithms of SU2 will be described with a particular emphasis on the methods used to produce the results in this paper. The convective and viscous fluxes were calculated using a second-order Roe scheme. The S-A turbulence model was used, with variables convected using a second-order upwind method. Venkatakrishnan's limiter is used. Implicit local time-stepping is used to converge the problem to a steady-state solution, and the linear system is solved using the GMRES method with a maximum error tolerance of $\mathcal{O}(10^{-10})$ for each nonlinear iteration of the flow solver. LU-SGS preconditioning was used.

\begin{wraptable}{r}{5.5cm}
  \begin{center}
  \begin{tabular}{||c|c||} \hline
    $M_\infty$ & $0.15$ \\ \hline 
    $Re_c$     & $6M$ \\ \hline
    $T_\infty$ & $300K$ \\ \hline
    $\alpha$ & $0^{\circ}$, $10^{\circ}$, $15^{\circ}$ \\ \hline
    $\mathcal{R}_{\tilde\nu}(U)$ & SA \\ \hline
  \end{tabular}
  \caption{NACA 0012 free-stream conditions.} \label{tab:naca0012_runconditions}
  \end{center}
\end{wraptable} 

The limiter uses a tunable coefficient and a characteristic length. In this work there values of the limiter coefficient were tested, 0.1, 1.0 and 10.0, along with variations in the CFL number to find appropriate values for each mesh. The limiter characteristic distance was chosen as 0.1 for the mesh with 257 points on the surface based on the recommendations of Venkatakrishan\cite{Venkatakrishnan:1993}. This value was scaled for the other meshes based on the number of surface points. The characteristic distance using this method can be found using $\Delta x_{char} = 25.7 c  / n_p $, where $n_p$ is the number of points on the surface and $c$ is the chord length.
A summary of the free-stream conditions used to model this problem are shown in Table~\ref{tab:naca0012_runconditions}. 



\input{./tex/Modeling}
\input{./tex/Numerics}
\input{./tex/Linear_Solver}
%\input{./tex/Optimization}
\input{./tex/Computational_Domain}




